Reviving the Lost Art of \\Combinator Graph Reduction

### 2023-01-28 experiments/superg/doc/paper/paper.tex
Plot for turner v. Miranda.

We use the Criterion~\cite{heisler_criterionrs_2023} benchmarking library to measure the performance of our engines and Miranda.
The original Miranda does not capture performance metrics, so we apply a small patch to the source code to output the time elapsed during a reduction operation.
The 20-line patch and instructions on how to apply it are included with the source code for our implementation.

@@

\begin{figure*}
    \includesvg[width=\textwidth]{turner_vs_miranda}
    \centering
    \caption{
        Time to execute the Fibonacci benchmark program on the original Miranda and our Miranda-style engine.
        A lower value on the Y-axis is better.}
    \label{fig:turner-vs-miranda}
\end{figure*}

>>>>

We use the Criterion~\cite{heisler_criterionrs_2023} benchmarking library to measure the performance of our engines and Miranda.
The original Miranda does not capture performance metrics, so we apply a small patch to the source code to output the time elapsed during a reduction operation.
The 20-line patch and instructions on how to apply it are included with the source code for our implementation.
We use Criterion's default measurement strategy: each benchmark runs repeatedly for 5 seconds as a warmup, after which 100 samples of the execution time are collected.
Finally, an estimate of the average execution time is computed using linear regression over the samples.

@@

\begin{figure}
    %\includesvg[width=\textwidth]{turner_vs_miranda}
    \begin{tikzpicture}
        \begin{axis}[
                title={Time to execute \texttt{fib} $n$},
                xlabel={Parameter $n$},
                xtick={10, 15, 20},
                ylabel={Execution time (in milliseconds)},
                ymin = 0,
                scaled y ticks = false,
                legend pos = north west,
            ]
            \addplot[
                color = blue,
                mark=square,
            ]
            coordinates {
                    (10.0, 0.18171432823529418)
                    (15.0, 1.7536414818181825)
                    (20.0, 17.489519720000008)
                };

            \addplot[
                color = red,
                mark=o,
            ]
            coordinates {
                    (10.0, 0.05903952613565834)
                    (15.0, 0.6745943900990098)
                    (20.0, 7.2472888442857135)
                };

            \legend{Miranda(original), Miranda-style Engine}

        \end{axis}
    \end{tikzpicture}
    \centering
    \caption{
        Time to execute the Fibonacci benchmark program on the original Miranda and our Miranda-style engine.
        A lower value on the Y-axis is better.}
    \label{fig:turner-vs-miranda}
\end{figure}
